%\documentclass[12pt,letterpaper,doublespaced,ETD,dvips]{gt-ece-thesis}
\documentclass[12pt,letterpaper,doublespaced,ETD]{gt-ece-thesis} %taking dvips out enable pdf bookmark generation as well as the logo printing on the first page

\title{Target Tracking Using Residual Vector Quantization}
\author{Salman Aslam}
\copyrightyear{2011}
\graddate{11 November, 2011}  
\approvaldate{11 November 2011}  

\addadvisor{Dr. Christopher F. Barnes}{Assoc. Professor, School of ECE}{Georgia Institute of Technology}
\addchair{Dr. David V. Anderson}{Assoc. Professor, School of ECE}{Georgia Institute of Technology}
\addreader{Dr. Aaron F. Bobick, Co-advisor}{Professor, School of Interactive Computing}{Georgia Institute of Technology}
\addreader{Dr. Vijay Madisetti}{Professor, School of ECE}{Georgia Institute of Technology}
\addreader{Dr. Patricio Vela}{Asst. Professor, School of ECE}{Georgia Institute of Technology}
\addreader{Dr. Santanu Dey}{Asst. Professor, School of ISYE}{Georgia Institute of Technology}


%\bibfiles{f:/salman/work/writing/MyCitations}
\bibfiles{MyCitations}

\titlepagetrue
\figurespagetrue
\tablespagetrue
\contentspagetrue
\symbolspagefalse
\glossarypagefalse 
\bibpagetrue
\mastersthesisfalse 
\multivolumefalse
\singlespacednotestrue


\usepackage{graphicx, subfigure, verbatim}
\usepackage{insfig}
\usepackage{url}
\usepackage{multirow}
\usepackage{hyperref}
%\usepackage{longtable}
\usepackage[usenames,dvipsnames]{color}
\definecolor{light-gray}{gray}{0.95}
\usepackage{amsmath,epsfig,verbatim,listings}
\lstset{breaklines=true,breakindent=0pt,
        prebreak=\mbox{\tiny$\searrow$},
        postbreak=\mbox{{\color{blue}\tiny$\rightarrow$}},
	tabsize=2,
linewidth=1.1\linewidth,
xleftmargin=-0.8in,
basicstyle=\tiny,
numbers=left,
frame=single,
captionpos=t,
title=\lstname,
backgroundcolor=\color{light-gray}}


\setchaptertocdepth{2}
\setappendixtocdepth{2}

\settocstring{Table of Contents}
\setlofstring{List of Figures}
%\setlotstring{List of Tables}
\setbibstring{References}
\setindstring{Index}
\setdedstring{Dedication}
\setglostring{List of Terms}
\setchpstring{Chapter}
\setappstring{Appendix}
\setprtstring{Volume}
\setabsstring{Summary}
\setlosstring{List of Symbols}
\setackstring{Acknowledgment}

\setfrontpagestyle{plain}
\setbodypagestyle{plain}
\setendpagestyle{plain}

\pagestyle{plain}
\bibliographystyle{ieeetr}