%\documentclass[12pt,letterpaper,doublespaced,ETD,proposal]{gt-ece-thesis} %use this line for proposal
\documentclass[12pt,letterpaper,doublespaced,ETD]{gt-ece-thesis} %use this line for thesis


\title{Multi-Target Tracking Using Residual Vector Quantization}
\author{Salman Aslam}
\copyrightyear{2010}
\graddate{December 2010}  
\approvaldate{December 2010}  

\addadvisor{Dr. Christopher F. Barnes}{Asst. Professor, School of ECE}{Georgia Institute of Technology}
\addchair{Dr. David V. Anderson}{Professor, School of ECE}{Georgia Institute of Technology}
\addreader{Dr. Aaron F. Bobick, Co-advisor}{Professor, School of Interactive Computing}{Georgia Institute of Technology}
\addreader{Dr. Vijay Madisetti}{Asst. Professor, School of ECE}{Georgia Institute of Technology}
\addreader{Dr. Patricio Vela}{Asst. Professor, School of ECE}{Georgia Institute of Technology}



\bibfiles{c:/salman/work/writing/MyCitations}

\titlepagetrue
\figurespagetrue
\tablespagetrue
\contentspagetrue
\symbolspagefalse
\glossarypagefalse 
\bibpagetrue
\mastersthesisfalse 
\multivolumefalse
\singlespacednotestrue


\usepackage{graphicx, subfigure}
\usepackage{insfig}
\usepackage{url}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{color}

\setchaptertocdepth{2}
\setappendixtocdepth{2}

\settocstring{Table of Contents}
\setlofstring{List of Figures}
%\setlotstring{List of Tables}
\setbibstring{References}
\setindstring{Index}
\setdedstring{Dedication}
\setglostring{List of Terms}
\setchpstring{Chapter}
\setappstring{Appendix}
\setprtstring{Volume}
\setabsstring{Summary}
\setlosstring{List of Symbols}
\setackstring{Acknowledgment}

\setfrontpagestyle{plain}
\setbodypagestyle{plain}
\setendpagestyle{plain}

\include{figs/inkscapeLatex}
\begin{document}
	
	\pagestyle{plain}
	\bibliographystyle{ieeetr}

	\begin{FrontMatter}
		\contents %Generates the TOC, LOF, and LOT
	\end{FrontMatter}
	\begin{dedication}
		To my parents, my wife, and my children
	\end{dedication}
	\begin{acknowledgement}
		Thanks to all \newpage
	\end{acknowledgement}
	%\begin{preface}
	%	hello
	%\end{preface}
	\begin{Body}	
		
%@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
\chapter{Introduction}
\label{chap_Introduction}	
%@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
\par
Images have fascinated humans for thousands of years.  The earliest cave paintings have been dated back to around 30,000 years \cite{2009_WEB_EarliestHumanPaintings_Gray}.  Currently, several fields 




%@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
\chapter{Tracking methods}
\label{chap_tracking_methods}	
%@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
%#######################		
\section{Introduction}
%#######################
a



%@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
\chapter{Conclusions}
\label{chap_Conclusions}	
%@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
b

%@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
\appendix{Appendices}
\label{app:AppendixA}
%@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
c










%##############################################################################################################
\end{Body}
\begin{EndMatter}
\references% Generates the bibliography page
\end{EndMatter}
\end{document}

%##############################################################################################################
%##############################################################################################################

